Network Origins of Social Distinction

### 2025-07-20 manuscript.tex
new edits

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.6\linewidth]{Plots/star-roles-by-size.png}
    \caption{Enter Caption}
    \label{fig:star-scaling}
\end{figure}

Another advantage of rescaling the $s_i$ component of equation~\ref{eq:distinction} is that it makes the distinction score of key nodes in the graph sensitive to network scaling, so that it increases when peripheral actors are added to the network. For instance, Figure~\ref{fig:star-scaling} illustrates the centrality score for star and peripheral nodes in star graphs of varying sizes. As we can see, when distinction is calculated simply as $\beta^*_i = s_i - \kappa_i$, the distinction score is a constant for the star nodes across graphs of different sizes, demonstrating insensitivity to network scaling. By way of contrast, when distinction is calculated as in Equation~\ref{eq:distinction}, then we observe that the distinction score of the star node increases logarithmically with network size, which is precisely what we want, as a star mediating between many peripheral nodes should be more distinct that a star mediating between just a few peripheral nodes.
